---
title: "Visuals 401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Visual 1: Variable Distributions ###
##DO EVERYTHING AGAIN WITH WEEKS!!!##

```{r}
#Importing Braodway_Avg
setwd('/Users/morganhogenmiller/Desktop/GitHub/DA_401/Data sets')
df=read.csv('Broadway_Avg.csv')
library(ggplot2)
library(reshape2)
library(dplyr)
library(plyr)
library(doBy)
library(survival)
library(survminer)
library(car)
colnames(df)
#Remove NA value from 
df=df[!(df$Category==0),]
df=na.omit(df, cols="LogWeeks")

count(df$Censored==0)

colnames(df)[colnames(df)=="Grand.Mean"] <- "Grand.Means.GT"
colnames(df)[colnames(df)=="First.Week"] <- "First.Mean.GT"
colnames(df)[colnames(df)=="Capacity..."] <- "Avg % Capacity Filled"


```

```{r Distribution of Weeks for Methods section}

ggplot(data=df, aes(Weeks)) + geom_density(fill='black') +ggtitle('Distribution of Total Weeks on Braodway') +xlab('Total Number of Weeks Show Survived')+ylab('Density') + theme(plot.title = element_text(hjust = 0.5))

summary(df$Weeks)
```


# Making Visuals for the Results section of the paper #




#Visual 1: Density plots#

```{r Density Plots for each variable of interest }
# Multiple histograms
#First, have to melt the data so that it sees each columns as calues in the variable column and their values in a seperate column
df_bw=df[c(4,9,12)]
melt.df <- melt(df_bw)

#Creating figure with multiple columns
ggplot(data = melt.df, aes(x = value)) + 
stat_density() + 
facet_wrap(~variable, scales = "free")  + ggtitle('Density Plots for Broadway Original Data Set Variables of Interest') + theme(plot.title = element_text(hjust = 0.5)) + xlab('Value') + ylab('Density')


```



```{r}

#First, have to melt the data so that it sees each columns as calues in the variable column and their values in a seperate column
#taking log of the total Tonys to normalize it

df_color=df[c(11,14,15,22,10,16)]
melt.df <- melt(df_color)

#Creating figure with multiple columns
ggplot(data = melt.df, aes(x = value)) + 
stat_density(fill='purple') + 
facet_wrap(~variable, scales = "free") + ggtitle('Density Plots for Variables Unique to Study') + theme(plot.title = element_text(hjust = 0.5)) + xlab('Value') + ylab('Density')

```


###Google Headlines relationship with Weeks ###
Correlation coefficients

```{r}
#Scatter plot of headlines v. weeks
ggplot(df) + aes(x=Sentimentality, y=Weeks) + geom_point()

#noticed potential outlier
boxplot(df$Sentimentality)

#isolating outlier
outliers <- boxplot(df$Sentimentality, plot=FALSE)$out
outliers

#deleting outliers
nooutliers<-df[-which(df$Sentimentality %in%outliers),]

nrow(nooutliers)

#Recreating the scatterplot without outliers
ggplot(nooutliers) + aes(x=Sentimentality, y=Weeks) + geom_point() + ggtitle("Google Headline Sentimentality v. Longevity")  + xlab("Google Headline Sentimentality Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))

```
Not much of a correlation between the overall search traffic and the sentimentality of Google headlines.





### Google Trends ###
do the same as above with both first week ...then work to get mean from month before and after Tony
```{r Google Trends}
#Scatter plot of grand search mean v. weeks
ggplot(df) + aes(x=Grand.Means.GT, y=Weeks) + geom_point()

#Distribution
boxplot(df$Grand.Mean)

#Recreating the scatterplot without outliers
ggplot(df) + aes(x=Grand.Means.GT, y=Weeks) + geom_point() + ggtitle("Google Trend Grand Mean v. Longevity") + theme(plot.title = element_text(hjust = 0.5)) + xlab("Google Trend Mean Search Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))

cor.test(df$Grand.Mean, df$Weeks)
```

```{r Google Trends}
#Scatter plot of grand search mean v. weeks
ggplot(df) + aes(x=First.Mean.GT, y=Weeks) + geom_point()

#Distribution
boxplot(df$First.Mean.GT)

#Recreating the scatterplot without outliers
ggplot(df) + aes(x=First.Mean.GT, y=Weeks) + geom_point() + ggtitle("Google Trend First Day Score v. Longevity") + theme(plot.title = element_text(hjust = 0.5)) + xlab("Google Trend Avg. First Week Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))

i=lm( Weeks~Sentimentality, data=df)
summary(i)
```

```{r Google Trends: Histograms of first and last months for shows}
gt=read.csv('/Users/morganhogenmiller/Desktop/GitHub/DA_401/Data sets/showfirstlast.csv')

#Distrubution of starting months

ggplot(data = gt, aes(first.month)) + 
geom_bar() + scale_x_discrete(name ="First Month", 
                    limits=c(1,2,3,4,5,6,7,8,9,10,11,12)) + ylab('Frequency')+ ggtitle('Distribution of Starting Months') + theme(plot.title = element_text(hjust = 0.5))

#Distribution of ending months
ggplot(data = gt, aes(last.month)) + 
geom_bar() + scale_x_discrete(name ="Last Month", 
                    limits=c(1,2,3,4,5,6,7,8,9,10,11,12)) + ylab('Frequency')+ ggtitle('Distribution of Closing Months') + theme(plot.title = element_text(hjust = 0.5))
```



Methods section for survival analysis


```{r Suvival Analysis for Tony Award Wins}


#Create variable for y/n to Tony awards
df$Tony_yn <- ifelse(df$total== 0,'No', 'Yes')


#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)
surv_object

#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Tony_yn, data = df)
summary(fit1)

#plot of the survival probability over time for Tony v. No Tonys
ggsurvplot(fit1, data = df, pval = TRUE) + xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities of Shows With and Without Tonys')

```


```{r Suvival Analysis for Tony Award Presence}


#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)
surv_object

#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Tony.Season, data = df)
summary(fit1)

#plot of the survival probability over time for Tony v. No Tonys
ggsurvplot(fit1, data = df, pval = TRUE) + xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities of Shows In and Out of Tony Season')

ggplot(data = df, aes(Tony.Season)) + 
geom_bar()

as.data.frame(table(df$Tony.Season))
```


```{r Suvival Analysis for Wikipedia Category}

#Recode categories from postive, negative, and neutral to 0,1,2
#df$Category <- ifelse(df$Category== "Positive",2,ifelse(df$Category== "Negative", 0, 1))

#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)
surv_object

#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Category, data = df)
summary(fit1)

#plot of the survival probability over time for Tony v. No Tonys
ggsurvplot(fit1, data = df, pval = TRUE) + xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities of Shows by Wikipedia Category Breakdown')

```


```{r Proportional Hazard Model}
#Proportional hazard model

#Making Tony season variable factor Y/N values


df$Tony.Season <- as.factor(df$Tony.Season)
df$Tony_yn <- as.factor(df$Tony_yn)
df$Category<-as.factor(df$Category)
fit.coxph <- coxph(surv_object ~  Capacity.... + Performances+Sentimentality + Grand.Means.GT + Tony_yn +Category +First.Mean.GT +Tony.Season,
                   data = df)
fit.coxph
#summary(fit.coxph)
ggforest(fit.coxph, data = df) + ggtitle('Cox Proportional Hazard Model Results')

#High censoring
#ggplot(df, aes(x=Censored)) + geom_histogram()
#Rearrange variables into strata to make this significant
```


```{r Checking assumptions for Cox model}

#PLOT THE DISTRIBUTION OF SURVIVAL RATES OVER TIME
#plot(survfit(mod.allison), ylim=c(0.7, 1), xlab="Weeks",
    #ylab="Proportion Not Rearrested")


cox.zph(fit.coxph)
```

```{r Model without the non proportional covariates}
fit.coxph2 <- coxph(surv_object ~   Sentimentality + Grand.Means.GT + Tony_yn +Category +Tony.Season,
                   data = df)

cox.zph(fit.coxph)
```

