---
title: "Visuals 401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Visual 1: Variable Distributions ###

```{r}
#Importing Braodway_Avg
setwd('/Users/morganhogenmiller/Desktop/GitHub/DA_401/Data sets')
df=read.csv('/Users/morganhogenmiller/Desktop/GitHub/DA_401/Data sets/Broadway_Avg.csv')
library(ggplot2)
library(reshape2)
library(dplyr)
library(plyr)
library(doBy)
library(survival)
library(survminer)
library(car)
colnames(df)
#Remove NA value from 
df=df[!(df$Category==0),]
df=na.omit(df, cols="LogWeeks")

#Create variable for y/n to Tony awards
df$Tony_yn <- ifelse(df$total== 0,0, 1)
table(df$Category)


colnames(df)[colnames(df)=="Grand.Mean"] <- "Grand Google Searches"
colnames(df)[colnames(df)=="First.Week"] <- "Week 1 Google Searches"
colnames(df)[colnames(df)=="Capacity..."] <- "Avg % Capacity Filled"
colnames(df)[colnames(df)=="Sentimentality"]<-"Google Headline Sentiment"
colnames(df)[colnames(df)=="Tony_yn"]<-"Tony_Win"
colnames(df)[colnames(df)=="Tony.Season"]<-"Tony_Eligibility"




```

```{r Distribution of Weeks for Methods section}

ggplot(data=df, aes(Weeks)) + geom_density(fill='black') + ggtitle("Distribution of Musicals' Survival on Braodway") +xlab('Musical Survival (Weeks)')+ ylab('Density') + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size=18),axis.title.x = element_text(size = 14),axis.title.y = element_text(size = 14)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))


summary(df$Weeks)
```


# Making Visuals for the Results section of the paper #




#Visual 1: Density plots#

```{r Density Plots for each variable of interest }
# Multiple histograms
#First, have to melt the data so that it sees each columns as calues in the variable column and their values in a seperate column
df_bw=df[c(4,9,12)]
melt.df <- melt(df_bw)

#Creating figure with multiple columns
ggplot(data = melt.df, aes(x = value)) + 
stat_density() + 
facet_wrap(~variable, scales = "free")  + ggtitle('Density Plots for Broadway Original Data Set Variables of Interest') + theme(plot.title = element_text(hjust = 0.5)) + xlab('Value') + ylab('Density')


```



```{r}

#First, have to melt the data so that it sees each columns as calues in the variable column and their values in a seperate column
#taking log of the total Tonys to normalize it

df2<-mutate(df, Wikipedia_Sentiment = ifelse(Category == "Positive", 2, ifelse(Category=="Neutral",1,0)))
df2

colnames(df2)[colnames(df2)=='Wikipedia_Sentiment']<-'Wikipedia Sentiment'
df_color=df2[c(11,26,14,15,25,16)]
melt.df <- melt(df_color)


#Creating figure with multiple columns
ggplot(data = melt.df, aes(x = value)) + 
stat_density(fill='black') + 
facet_wrap(~variable, scales = "free") + ggtitle('Important Variable Densities') + theme(plot.title = element_text(hjust = 0.5,size=18),axis.title.x = element_text(size = 16),axis.title.y = element_text(size = 16),strip.text.x = element_text(size=11)) + xlab('Variable') + ylab('Density') +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) 

```


###Google Headlines relationship with Weeks ###
Correlation coefficients

# ```{r}
# #Scatter plot of headlines v. weeks
# ggplot(df) + aes(x=Sentimentality, y=Weeks) + geom_point()
# 
# #noticed potential outlier
# boxplot(df$Sentimentality)
# 
# #isolating outlier
# outliers <- boxplot(df$Sentimentality, plot=FALSE)$out
# outliers
# 
# #deleting outliers
# nooutliers<-df[-which(df$Sentimentality %in%outliers),]
# 
# nrow(nooutliers)
# 
# #Recreating the scatterplot without outliers
# ggplot(nooutliers) + aes(x=Sentimentality, y=Weeks) + geom_point() + ggtitle("Google Headline Sentimentality v. Longevity")  + xlab("Google Headline Sentimentality Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))
# 
# ```
Not much of a correlation between the overall search traffic and the sentimentality of Google headlines.





### Google Trends ###
do the same as above with both first week ...then work to get mean from month before and after Tony
# ```{r Google Trends}
# #Scatter plot of grand search mean v. weeks
# ggplot(df) + aes(x=Grand.Means.GT, y=Weeks) + geom_point()
# 
# #Distribution
# boxplot(df$Grand.Mean)
# 
# #Recreating the scatterplot without outliers
# ggplot(df) + aes(x=Grand.Means.GT, y=Weeks) + geom_point() + ggtitle("Google Trend Grand Mean v. Longevity") + theme(plot.title = element_text(hjust = 0.5)) + xlab("Google Trend Mean Search Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))
# 
# cor.test(df$Grand.Mean, df$Weeks)
# ```

```{r Google Trends}
#Scatter plot of grand search mean v. weeks
# ggplot(df) + aes(x=First.Mean.GT, y=Weeks) + geom_point()
# 
# #Distribution
# boxplot(df$First.Mean.GT)
# 
# #Recreating the scatterplot without outliers
# ggplot(df) + aes(x=First.Mean.GT, y=Weeks) + geom_point() + ggtitle("Google Trend First Day Score v. Longevity") + theme(plot.title = element_text(hjust = 0.5)) + xlab("Google Trend Avg. First Week Score") + ylab("Weeks") + theme_minimal(base_family = 'serif') + theme(plot.title = element_text(hjust = 0.5))
# 
# i=lm( Weeks~Sentimentality, data=df)
# summary(i)
```

```{r Google Trends: Histograms of first and last months for shows}
# gt=read.csv('/Users/morganhogenmiller/Desktop/GitHub/DA_401/Data sets/showfirstlast.csv')
# 
# #Distrubution of starting months
# 
# ggplot(data = gt, aes(first.month)) + 
# geom_bar() + scale_x_discrete(name ="First Month", 
#                     limits=c(1,2,3,4,5,6,7,8,9,10,11,12)) + ylab('Frequency')+ ggtitle('Distribution of Starting Months') + theme(plot.title = element_text(hjust = 0.5))
# 
# #Distribution of ending months
# ggplot(data = gt, aes(last.month)) + 
# geom_bar() + scale_x_discrete(name ="Last Month", 
#                     limits=c(1,2,3,4,5,6,7,8,9,10,11,12)) + ylab('Frequency')+ ggtitle('Distribution of Closing Months') + theme(plot.title = element_text(hjust = 0.5))
```



Methods section for survival analysis


```{r Suvival Analysis for Tony Award Wins}

#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)


#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Tony_Win, data = df)


#plot of the survival probability over time for Tony v. No Tonys
ggsurv1<-ggsurvplot(fit1, data = df, palette = c("#000000",	"#DAA520"), legend=c(.8,.8),pval = NULL, legend.title = "Legend", legend.labs=c('No Tony Wins','Tony Wins'), font.title=c(18), font.legend=c(18), font.x=c(18), font.y=c(18), font.main=c(18)) + xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities Over Time Relative to Tony Wins') 
#+ scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))

ggsurv1

ggsurv1$plot <- ggsurv1$plot +  ggplot2::annotate("text",  x = 320, y = 0.65, label = "p-value: 0.00017", size = 5)

ggsurv1

```


```{r Suvival Analysis for Tony Award Presence}


#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)
surv_object

#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Tony_Eligibility, data = df)
summary(fit1)

#plot of the survival probability over time for Tony v. No Tonys
ggsurv2<-ggsurvplot(fit1, data = df, palette = c("#000000",	"#DAA520"),  pval = NULL, legend=c(.65,.8),legend.title = "Legend", legend.labs=c('Not Eligible for Tony Nominations','Eligible for Tony Nominations'), font.title=c(18), font.legend=c(18), font.x=c(18)) + xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities Over Time Relative to Tony Eligibility')

ggsurv2$plot <- ggsurv2$plot +  ggplot2::annotate("text",  x = 180, y = 0.65, label = "p-value < 0.0001", size = 5)

ggsurv2
summary(ggsurv2$plot)

ggplot(data = df, aes(Tony.Season)) + 
geom_bar()

as.data.frame(table(df$Tony.Season))
```


```{r Suvival Analysis for Wikipedia Category}

#Recode categories from postive, negative, and neutral to 0,1,2
#df$Category <- ifelse(df$Category== "Positive",2,ifelse(df$Category== "Negative", 0, 1))

#create survival object
surv_object <- Surv(time = df$Weeks, event = df$Censored)
surv_object

#Fitting the survival object to a Kaplan-Meir curve
fit1 <- survfit(surv_object ~ Category, data = df)
summary(fit1)

#plot of the survival probability over time for Tony v. No Tonys
ggsurv3<- ggsurvplot(fit1, data = df,legend=c(.75,.8), palette = c("#FF0000","#000000",	"#DAA520"), legend.title = "Legend", legend.labs=c('Negative Summary','Neutral Summary','Positive Summary'), font.title=c(16), font.legend=c(16), font.x=c(16) , font.y=c(16)) +  xlab(' Number of Weeks') + ylab('Survival Probability') + ggtitle('Survival Probabilities Over Time Relative to Wikipedia Summary')

ggsurv3$plot <- ggsurv3$plot +  ggplot2::annotate("text",  x = 287, y = 0.60, label = "p-value < 0.0001", size = 5)
ggsurv3




```


```{r Proportional Hazard Model}
#Proportional hazard model

#Making Tony season variable factor Y/N values


df$Tony.Season <- as.factor(df$Tony.Season)
df$Tony_yn <- as.factor(df$Tony_yn)
df$Category<-as.factor(df$Category)
fit.coxph <- coxph(surv_object ~  Capacity.... + Performances+Sentimentality + Grand.Means.GT + Tony_yn +Category +First.Mean.GT +Tony.Season,
                   data = df)
fit.coxph
#summary(fit.coxph)
ggforest(fit.coxph, data = df) + ggtitle('Cox Proportional Hazard Model Results')

#High censoring
#ggplot(df, aes(x=Censored)) + geom_histogram()
#Rearrange variables into strata to make this significant
```


```{r Checking assumptions for Cox model}

#PLOT THE DISTRIBUTION OF SURVIVAL RATES OVER TIME
#plot(survfit(mod.allison), ylim=c(0.7, 1), xlab="Weeks",
    #ylab="Proportion Not Rearrested")


cox.zph(fit.coxph)
```

```{r Model without the non proportional covariates}
fit.coxph2 <- coxph(surv_object ~   Sentimentality + Grand.Means.GT + Tony_yn +Category +Tony.Season,
                   data = df)

cox.zph(fit.coxph)
```



